Augmentation of a Historical Harpsichord Keyboard Replica for Haptic-Enabled Interaction in Museum Exhibitions

### 2025-01-25 nime-paper-template.tex
abstract versions

%%
%% This is file `sample-nime-paper.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-nime-paper.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% History of NIME Template Updaters:
%% Modified by Florent Berthaut, Charles Martin, Yichen Wang, 21 November 2024
%% Modified by Adnan Marquez-Borbon 30 November 2022
%% Modified by Courtney Reed 28 November 2022
%% Modified by Joe Wright 14 December 2019
%% Modified by Niccolò Granieri 10 October 2018
%% Modified by Angelo Fraietta 23 December 2018
%% Modified by Angelo Fraietta 22 November 2018
%% Modified by Rodrigo Schramm on 22 September 2018
%% Modified by Luke Dahl on 17 October 2-17
%% Modified by Cumhur Erkut on <2016-10-11 Tue>
%% Modified by Edgar Berdahl on 5 November 2014
%% Modified by Baptiste Caramiaux on 25 November 2013
%% Modified by Kyogu Lee on 7 October 2012
%% Modified by Georg Essl on 7 November 2011
%%
%% And here's the template:
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{nimeart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{nimeart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf,anonymous,review]{nimeart}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

>>>>

%%
%% This is file `sample-nime-paper.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-nime-paper.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% History of NIME Template Updaters:
%% Modified by Florent Berthaut, Charles Martin, Yichen Wang, 21 November 2024
%% Modified by Adnan Marquez-Borbon 30 November 2022
%% Modified by Courtney Reed 28 November 2022
%% Modified by Joe Wright 14 December 2019
%% Modified by Niccolò Granieri 10 October 2018
%% Modified by Angelo Fraietta 23 December 2018
%% Modified by Angelo Fraietta 22 November 2018
%% Modified by Rodrigo Schramm on 22 September 2018
%% Modified by Luke Dahl on 17 October 2-17
%% Modified by Cumhur Erkut on <2016-10-11 Tue>
%% Modified by Edgar Berdahl on 5 November 2014
%% Modified by Baptiste Caramiaux on 25 November 2013
%% Modified by Kyogu Lee on 7 October 2012
%% Modified by Georg Essl on 7 November 2011
%%
%% And here's the template:
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{nimeart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{nimeart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf]{nimeart}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

\begin{itemize}
  \item
  \emph{Repository one}: \url{https://www.github/com/organisationthatslong/everslightlytoo-long-repository-name-1}
  \item
  \emph{Repository two}: \url{https://www.github/com/organisationthatslong/everslightlytoo-long-repository-name-2}
  \item
  \emph{Repository three}: \url{https://www.github/com/organisationthatslong/everslightly-too-long-repository-name-3}
\end{itemize}

### 2025-01-25 src/main.tex
abstract versions

%%
%% This is file `sample-nime-paper.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-nime-paper.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% History of NIME Template Updaters:
%% Modified by Florent Berthaut, Charles Martin, Yichen Wang, 21 November 2024
%% Modified by Adnan Marquez-Borbon 30 November 2022
%% Modified by Courtney Reed 28 November 2022
%% Modified by Joe Wright 14 December 2019
%% Modified by Niccolò Granieri 10 October 2018
%% Modified by Angelo Fraietta 23 December 2018
%% Modified by Angelo Fraietta 22 November 2018
%% Modified by Rodrigo Schramm on 22 September 2018
%% Modified by Luke Dahl on 17 October 2-17
%% Modified by Cumhur Erkut on <2016-10-11 Tue>
%% Modified by Edgar Berdahl on 5 November 2014
%% Modified by Baptiste Caramiaux on 25 November 2013
%% Modified by Kyogu Lee on 7 October 2012
%% Modified by Georg Essl on 7 November 2011
%%
%% And here's the template:
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{nimeart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{nimeart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf]{nimeart}
\usepackage{graphicx,subcaption}
% \usepackage{tikz}
% \usetikzlibrary{shapes,arrows}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
% This work describes the design of an electronically augmented replica of a
% 16th-century harpsichord keyboard with a typical Renaissance Italian layout to create a DMI. The
% project is a collaboration between the \anon{NEMUS project} and the Museo di San Colombano,
% which houses the Tagliavini Collection of playable historical keyboard instruments. 
% The keyboard was commissioned for exhibition where it will act as an interface to digitised version of historical instruments that are not available to play by visitors.

% The project aims to enhance the experiential authenticity of the collection and address how we can conserve the interaction with historical instruments when the interface is a limiting factor in the verisimilitude of the experience playing a digitised instrument.

% The tactile feedback of the keyboard is created by incorporating the same mechanics of a two-register harpsichord with a single manual. 
% Unpitched strings under tension replicate the mechanical resistance characteristic of the original compass. 
% An array of optical sensors connected to a microcontroller was installed within the interface to generate continuous
% streams of data corresponding to the vertical motion of each jack. 
% This paper details the keyboard's design principles, technical development, and the motivations behind them.

This paper describes the design and creation of an electronically augmented replica of a 16th-century harpsichord keyboard with a typical Renaissance Italian layout in order to create a DMI. % [1]
The keyboard was commissioned for exhibition in a musical instrument museum where it will act as an interface to digitised versions of historical instruments that are not in a playable condition. % [2]
This project also addresses how we can interact with digitally conserve historic musical instruments when the interface is a limiting factor to the verisimilitude of the experience. % [2,3]
This ultimately culminated in a design for an interface capable of new expressions by extending, rather than forfeiting, the characteristics of the original. % [4]

@@

>>>>

%%
%% This is file `sample-nime-paper.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-nime-paper.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% History of NIME Template Updaters:
%% Modified by Florent Berthaut, Charles Martin, Yichen Wang, 21 November 2024
%% Modified by Adnan Marquez-Borbon 30 November 2022
%% Modified by Courtney Reed 28 November 2022
%% Modified by Joe Wright 14 December 2019
%% Modified by Niccolò Granieri 10 October 2018
%% Modified by Angelo Fraietta 23 December 2018
%% Modified by Angelo Fraietta 22 November 2018
%% Modified by Rodrigo Schramm on 22 September 2018
%% Modified by Luke Dahl on 17 October 2-17
%% Modified by Cumhur Erkut on <2016-10-11 Tue>
%% Modified by Edgar Berdahl on 5 November 2014
%% Modified by Baptiste Caramiaux on 25 November 2013
%% Modified by Kyogu Lee on 7 October 2012
%% Modified by Georg Essl on 7 November 2011
%%
%% And here's the template:
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{nimeart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{nimeart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf]{nimeart}
% \documentclass[sigconf,anonymous,review]{nimeart}
\usepackage{graphicx,subcaption}
% \usepackage{tikz}
% \usetikzlibrary{shapes,arrows}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}

%% Version 1
This paper describes the design and creation of an electronically augmented replica of a 16th-century harpsichord keyboard with a typical Renaissance Italian layout to create a digital musical instrument. % [1]
The keyboard was commissioned for exhibition in a musical instrument museum as an enhancement to the visitor experience by providing an interface to digitised versions of instruments within the collection. % [2]
This project also addresses how we can interact with digitally conserve historic musical instruments when the interface is a limiting factor to the verisimilitude of the experience. % [2,3]
This ultimately culminated in a design for an interface capable of new expressions by extending, rather than forfeiting, the characteristics of the original. % [4]

@@

%% Version 2
% This paper describes the design and creation of an electronically augmented replica of a 16th-century harpsichord keyboard with a typical Renaissance Italian layout to create a vibrotactile digital musical instrument. % [1]
% An array of optical sensors connected to a microcontroller was installed within the interface to generate continuous streams of data corresponding to the vertical motion of each jack. % [1, ~4]
% The keyboard was commissioned for exhibition in a musical instrument museum as an enhancement to the visitor experience by providing an interface to digitised versions of instruments within the collection.

% This project embodies the entanglement between musical instrument cultural heritage and its relationship with new and increasing accessible technologies. [3, 4]
% Acknowledgment and conscientiousness to older designs and aesthetics have been used in service of, rather than obstruction to, richer interactions with digital musical instruments.[2,3,4]
% This ultimately culminated in a design for an interface capable of new expressions by extending, rather than forfeiting, the characteristics of the original. % [4]
% We outline the details of the keyboard's design principles, technical development, and the motivations behind them. % [1]
